% Common Setup and Definitions
\setupinteraction[state=start,
	title={Evgeniy N. Sharapov},
	subtitle={R\'esum\'e},
	author={Evgeniy N. Sharapov},
	keyword={resume},
	% disable coloring of the links
	color=,
	style=\tf
]
\setuppapersize[letter][letter]
\setupbodyfont[Palatino, 9pt]
\definefontsynonym[Sans][Optima]
\definefontsynonym[Mono][Iosevka]
        
\definecolor[darkBlue][h=264E7F]
\definecolor[veryDarkBlue][h=00397F]
\definecolor[lightBlue][h=3E80B2]
\definecolor[veryLightBlue][h=DEEBFD]

% FontAwesome Glyphs 
\definefontsynonym[FontAwesome][fontawesome]
\definesymbol[phone][\getglyph{FontAwesome}{\char61589}]
\definesymbol[mobile][\getglyph{FontAwesome}{\char61707}]
\definesymbol[email][\getglyph{FontAwesome}{\char61664}]
\definesymbol[globe][\getglyph{FontAwesome}{\char61612}]
\definesymbol[github][\getglyph{FontAwesome}{\char61595}]
\definesymbol[linkedin][\getglyph{FontAwesome}{\char61665}]
\definesymbol[bitbucket][\getglyph{FontAwesome}{\char61809}]
\definesymbol[stackoverflow][\getglyph{FontAwesome}{\char61804}]
\definesymbol[twitter][\getglyph{FontAwesome}{\char61593}]
\definesymbol[check][{\scale[height=.4\bodyfontsize]\getglyph{FontAwesome}{\char61452}}]

\useURL[gmail][mailto:evgeniy.sharapov@gmail.com][][evgeniy.sharapov@gmail.com]
\useURL[linkedin][http://www.linkedin.com/in/evgeniysharapov][][{\symbol[linkedin] linkedin/in/evgeniysharapov}]
\useURL[bitbucket][https://bitbucket.org/evgeniysharapov][][{\symbol[bitbucket] bitbucket/evgeniysharapov}]
\useURL[github][https://github.com/evgeniysharapov][][{\symbol[github] github/evgeniysharapov}]
\useURL[stackoverflow][http://stackoverflow.com/users/338701/evgeniysharapov][][{\symbol[stackoverflow] stackoverflow/evgeniysharapov}]
\useURL[twitter][https://twitter.com/evgeniysharapov][][{\symbol[twitter] @evgeniysharapov}]


% Two Column paragraphs
\defineparagraphs[TwoColumn][n=2]
\setupparagraphs[TwoColumn][1][width=0.6\textwidth]
\defineparagraphs[InsideColumns][n=2]
\setupparagraphs[InsideColumns] [2]  [align=flushright]
\setupparagraphs[InsideColumns] [each]  [after={\blank[0em]}]

% name, address, phone, email
\define[3]\Contact{{\scd\color[darkBlue]{#1}}
  \blank
  \hbox{
  {\lower.2ex\hbox{\symbol[phone]} {\tf #2} {\bf\cdot} \lower.2ex\hbox{\symbol[email]} {\tf #3 }}
}}

% position, company, location, dates
\define[5]\Position{%
  \startInsideColumns
  {\goto{\bf #2}[#5]} \crlf
  {\it #1}
  \InsideColumns
  \hbox to 1em {
    #3}
  \hbox to 1em {
    #4}
  \stopInsideColumns%
}

% setup item lists
\setupitemgroup[itemize][each][packed,joinedup][symbol=check,before=]

\definelayout[cover][
  topspace=0cm,
  top=0cm,
  backspace=1cm,
  margin=1cm,
  rightedge=0cm,
  rightmargin=0.5cm,
  width=fit,
  height=fit,
  header=0.5cm,
  footer=0.5cm,
  ]
  
\definemakeup[cover]


\starttext

%% Debugging
\showlayout
\showboxes
\showframe
\showgrid
%% end of debugging


%% Front Page (short resume)

\startcovermakeup

\setuphead[subject][textstyle=cap]

%    Fancy Header
\startcombination[2, distance=0.01\textwidth]
	% contact
	{\framed[width=0.6\textwidth,align=flushleft,frame=off]{% !important
		\Contact
			{Evgeniy N. Sharapov}
			{(630) 448-0827}
			{\from[gmail]}
                      }}{}
	% social
	{\framed[width=0.39\textwidth, align=flushleft,
			background=color, backgroundcolor=veryLightBlue,frame=off,
			backgroundcorner=round, backgroundradius=1ex,
			offset=1ex]{\noindent
		{\bf \from[linkedin]} \crlf
		%{\bf \from[twitter]} \crlf
		{\bf \from[github]} \crlf
		{\bf \from[bitbucket]} \crlf
		{\bf \from[stackoverflow]}}}{}
\stopcombination
\hairline

% First Column
\startTwoColumn
\subject{Relevant Experience}

\Position{Senior Consultant}{Avanade}{Raleigh, NC}{Aug, 2014 -- }{avanade}
Fullstack design and development of  a platform for building and configuring applications for life insurance business arm of Metlife in Japan. Main objective configurability and ease of use for customers as well as reliability and security. Major involvement in deployment process using Docker, Jenkins and Azure services

\Position{Sr. Software Development Engineer}{StoneRiver, Inc}{Orlando, FL}{Apr, 2013 -- Aug, 2014 }{stoneriver}
Support and development of the software product for mid-size workers comp insurance companies. Fullstack development on Java, AS/400 and JBoss/Wildfly platforms. Customer support and customization. Test and release process using automation tools.  

\Position{Developer}{Click2Interact}{Orlando, FL}{Sep, 2012 -- Jan, 2013}{click}
Design and implementation of teacher-parent communication applicaiton for pre-schools. Fullstack development using Ruby on Rails framework, JavaScript and Clojure. 

\Position{Software Development Engineer}{Prognoz}{Perm, Russia}{Mar, 2012 -- Jul, 2012}{prognoz}
 Development of an ``Electronic Government'' platform based on IBM BPM and end-user web-application using GWT. Fullstack development with a strong focus on web-services and development for BPM.

\Position{Consultant/Programmer Analyst}{Marlabs Inc.}{Orlando, FL}{Mar, 2007 -- Dec, 2012}{marlabs}
Consulting work at Siemens Shared Services, where I worked on multiple projects developing custom vendor management application, documents management application, FileNet migration tools, scan and recognize application, application for customs compliance control, etc., and Team Disney. 

\Position{Engineer}{Fermi National Accelerator Lab}{Batavia, IL}{2001, 2002, 2004; Jan, 2005 -- Aug, 2005}{fermilab}
Multiple internships and then engineering position at the high-energy physics project. Helped to design and implement various tools and applications used for data acquisition and control. 

\Position{Software Developer}{InfoTelecom, LLC}{Perm, Russia}{Oct, 2003 -- Jul, 2004}{infotelecom}
Worked on the product software - highly customizable system of web-traffic statistics and monitoring. Back-end development on Oracle using PL/SQL and Java. 

\Position{Software Developer}{iTech Software}{Perm, Russia}{Oct, 2002 -- Sep, 2003}{itech}
Developed software for telecommunication company. Have been doing both high-level and low-level programming using C and Java.

% Second Column
\TwoColumn

\subject{\goto{Skills}[skills]}
\startitemize
\item Java, Groovy, JavaScript, Python, Clojure, Ruby, C/C++
\item Mongo, MS SQL, MySQL, Oracle, BerkleyDB
\item Spring, Apache Camel, JBoss Drools, Spring, iBatis, Websphere AS, JBoss AS, Wildfly
\item Docker, Azure
\item Mercurial, Git, Subversion, JIRA
\item Maven, Gradle, Ant, soapUI, RobotFramework, Jenkins 
\item HTML5, CSS, SASS/LESS, AngularJS, Webpack, React, Rails
\stopitemize

\subject{Education}
\startitemize
\item M.Eng. Industrial Engineering, {\unhyphenated Lehigh University}
\item B.Eng. Automated Control Systems, Perm State Technical University, Russia
\stopitemize

\subject{Books}
\startnarrower
{Instant Apache Camel Messaging System}, {\em Packt Publishing}, 2013, ISBN 9781782165347 
\stopnarrower

\subject{Certification}
\startitemize
\item Sun Certified Programmer for Java \crlf (CX-310-035) 
\item Sun Certified Web Component Developer \crlf (CX-310-081)
\stopitemize

\subject{Languages}
\startnarrower
English, Russian
\stopnarrower

\stopTwoColumn
\stopcovermakeup


%% Rest of the resume
\setupheadertexts[{\cap Evgeniy N. Sharapov}]
\setupfootertexts[\pagenumber]
\setuphead[subject][textstyle=cap]
\subject[skills]{Technical Skills}
\startitemize
\item {\bf Programming:} Java, Groovy, Python, JavaScript, Clojure, Ruby, C/C++ 
\item {\bf Development:} Eclipse, NodeJS, Maven, Ant, Mercurial, Git, SVN, JIRA, Jenkins 
\item {\bf Database:}  Mongo, MS SQL Server 2000/2005, Oracle 9i/10g, SQLite, MySQL.
\item {\bf Technologies:}   Docker, Azure, Apache Camel, JNI, Swing, SWT, Java 2D, RMI, EJB, JTA, JMS, JNDI, JDBC, JSP, Servlets, XML-RPC, XML, XSLT, XPath, JAX-RPC, WSDL4J, Axis, Hibernate, JBoss Drools, Websphere 5/6, JBoss AS, IBM Websphere Process Server, IBM Business Process Manager.
\item {\bf Web:} AngularJS, React, Webpack, HTML5, CSS3, Less, SASS
\stopitemize


% same as Position but different
\define[4]\Employment{
  \blank
	\setupframed[height=1cm,frame=off]
	\startcombination[2]
		{\framed[width=12cm,top=\vss,bottom=\vss,align=right]{%
		{\reference[#4]{}\sans \bfa #1}\\
		{\sans \sc #2}
		}}{}
		{\framed[width=5cm,align=flushright,top=\vss,bottom=\vss]{%
		{\sans \bf #3}
		}}{}
	\stopcombination
}
      
\Employment{Avanade ( Infusion until 2017)  --  Raleigh, NC}
{Senior Consultant}
{Aug~2014~--Present}
{avanade}
Designed, built and configured a platform for building and configuring applications for life insurance business arm of Metlife in Japan. Main objective configurability and ease of use for customers as well as reliability and security. Major involvement in deployment process using Docker, Jenkins and Azure services
\startitemize
\item Implementation and maintainance of the configuration application (Composer) using Node.Js, AngularJS, React and Mongo
\item Design and architecture of the back-end utilizing reactive streams (Reactor) to achieve better performance and scalability.
\item Design and implementation of application Groovy scripting, testing frameworks, loading and data migration tools.
\item Organization of CI process based on Docker containers.
\item Management of development process through JIRA, Jenkins, Stash, VSTS
\item Education and training of engineering teams; technical interviewing of candidates for Metlife and Infusion and recruitment on campus (UNC).
\stopitemize
Mongo; Java; Spring, Reactor, Groovy; JavaScript; NodeJS; Docker; Shell Scripts; AngularJS; React; HTML5; Less; JIRA

\Employment{Stone River, Inc -- Orlando, FL}
{Senior Software Development Engineer}
{Apr 2013~-–~Aug 2014}
{stoneriver}
Supported existing software systems and developed new solutions for mid-side workers comp insurance companies. Among other things tasks included: customer and technical support for multiple applications; organization and execution of third party software compatibility testing using Selenium; development of user interface, back-end processes and auxiliary scripting; organization of the testing and release process.
\startitemize
\item Customer and technical support for multiple applications.
\item Organization and execution of third party software compatibility testing using Selenium.
\item Development of user interface, back-end processes and auxiliary scripting
\item Organization of the testing and release process.
\stopitemize
Websphere AS 7; JBoss 5, 6; Wildfly 8; AS/400; MS SQL Server; Java; Hibernate 3.5;  Python; HTML5; Javascript;

\Employment{Click2Interact -- Orlando, FL}
{Developer}
{Sep 2012 -- Jan 2013}
{click}
Design and development of an educational platform for child development centers and pre-schools.

\startitemize
\item Design and implementation of the back-end server code using Ruby On Rails framework
\item Database design and business model prototyping. Researched the planetarium, its potential partners, and its competitors
\item User interface using Twitter Bootstrap, jQuery and HTML5.Pitched a cohesive campaign idea and ways to activate it
\stopitemize
Ruby On Rails 3.2, MySQL, RESTful Web-Services, Rackspace Cloud, jQuery, Twitter Bootstrap,

\Employment{Prognoz -- Perm Russia}
{Software Engineer}
{Mar 2012 –- Jul 2012}
{prognoz}
\startitemize
\item Tuning, installation and configuration of the IBM Websphere Process Server and Business Process Manager in cluster environment.
\item Development of the business process integration in Integration Designer.
\item Development of the “Meetings” application for the Moscow Government (documents exchange, meetings and appointments scheduling, notification services) for mobile and desktop platform.
  http://www.prognoz.com/
\stopitemize
Java 1.6, GWT, JPA 2, Web-Services, IBM Websphere Process Server and IBM BPM 8

\Employment{Marlabs -- Orlando, FL}
{Consultant/Programmer Analyst}
{Mar 2007 –- Dec 2012}
{marlabs}


\define[3]\Client{
  \blank
  \setupframed[frameoff]
  \startcombination[2]
  {\framed[width=12cm,top=\vss,bottom=\vss,align=right]{%
      {\sans \bf Client: #1}\\
      {\sans \bf Project #2}
    }}{}
  {\framed[width=5cm,align=flushright,top=\vss,bottom=\vss]{%
      {\bf #3}
    }}{}
   \stopcombination
}

\Client{Siemens Shared Services}
{Siemens Compliance  - SICOM (USA, Germany)}
{Nov 2010 –- Dec 2012}
\startitemize
\item Analysis of the business requirements and prototyping
\item Changes in user interface of the applications (JavaScript, HTML, CSS)
\item Changes in back-end processes (Java, T-SQL, Drools, XSLT) directed to a better performance, reliability, and scalability of the back end data processing
\item Migration of the application in SICOM stack to a new application platform (SQL Server 2005, WebSphere 6.1) to a different location (both software and hardware transition)
\item Optimization of development and release cycle  - quicker builds and deployment
\stopitemize
Java 5, RAD 7.5, Eclipse Platform, Drools, SQL Server 2000/2005, WebSphere 5.1/6.1, Javascript, CSS, HTML, XML/XSLT

\Client{Team Disney}
{Disney One Air Project (Improvements of SBC Booking and Reservation system)}
{Apr 2010 –- Oct 2010}
\startitemize
\item Analysis of business and technical requirements; prototyping
\item Implementation of Secure Flight requirements for air booking
\item Changes to existing data model, EJB, user interfaces (HTML, CSS, Javascript)
\item Integration testing of changes to existing applications (A La Carte, SBC)
\item Shell/Perl/AWK scripts for error detection and post incident analysis (parsing and analysis of log files)
\item Triaging, troubleshooting the incidents, fixing, testing, integration (full maintenance cycle)
\item On call support for the applications
\stopitemize
Java 5, RAD 7.5, JSF, Struts,  HTML, JavaScript, jQuery, Oracle 10g, Websphere 6, JBoss AS,  EJB, jQuery, MQ Series, Ant, ClearCase, AIX, Shell/AWK/Sed scripting, Perl

\Client{Siemens Shared Services}
{Project: Global Services Customs Declaration application that allows users to clear up shipments for import/export operations}
{Nov 2010 –- Dec 2012}
\startitemize
\item Analysis of business requirements
\item Organization of development team meetings and conference calls
\item Wrote technical specification for web services (WSDL and WSDD)
\item Designed front end using Java Servlets, JSP, HTML, CSS, and Javascript using AJAX technology
\item Configuration of iBatis ORM and Spring Framework
\item Design and implementation of business logic and data processing routes using Apache Camel
\item Wrote business rules using Drools and business logic processing customs declarations
\item Data transformation between DIN5 CUSDEC formats
\item Created Junit tests and Ant build scripts
\item Tested integration with logistic companies (Kuhne\& Nagel, DHL, Fedex)
\stopitemize
  Java 5, Apache Axis, Apache Camel, JBoss, Drools, Spring 2.5, Apache iBatis, MS SQL Server 2000, T-SQL, WebSphere 6, XML/XSLT, jQuery, Subversion, Ant, soapUI

\Client{Siemens Shared Services}
{Paperless invoicing application}
{May 2008 –- Jun 2009}
\startitemize 
\item Worked closely with third party companies (ScanOne, DirectInsite) and with business clients (Siemens Operating Companies)
\item Wrote technical specification for processing invoice information
\item Data transformation to/from OAGIS, DIN 5, EzAP formats
\item Database design for the invoices images storage on MS SQL Server 2005
\item Developed business rules engine (table driven), and its front end accessible by the business clients
\item Developed high performance TIFF library based on libtidd JAI and ImageIO
\item Tools for extracting invoice image data from Filenet into application database
\item Integration of the paperless invoice processing application with existing AR/AP applications
\item Organization of source code management using Subversion
\item Created Junit tests and Ant build scripts
\item Integration testing with outsource scanning/processing companies (ScaneOne, DirectInsite)
\stopitemize  
Java 5, Apache Camel, Spring 2.5, Apache iBatis, MS SQL Server 2000, T-SQL, WebSphere 6, XML/XSLT, jQuery, Subversion, Ant

\Client{Siemens Shared Services}
{Invoice Management Application}
{May 2007 –- Apr 2008}
\startitemize
\item Developed vendor management module based with front-end on Struts and Javascript.
\item Wrote transformation of vendor/invoice data to/from XML,CSV, EDI, DIN5 formats.
\item Designed data validation and consistency checks using Java and XML Schemas
\item Tuned application and database performance using caching, using NIO, queries optimization, indexes.
\item Designed and implemented application usage statistics based on Javascript and HTTP logs.
\item Developed web-based tools for testing using Python (Pylons), HTML and Javascript.
\item Wrote integration of the application with SAP (Spiridon) using JCo.
\item Created JUnit tests and Ant build scripts.
\stopitemize
Java 1.4,  MS SQL Server 2000, T-SQL, XML/XSLT, Struts, Websphere 5, Python, HTML, JavaScript, Ant,


\Employment{Fermi National Accelerator Laboratory -- Batavia, IL}
{Engineer}
{Jan 2005 -- Aug 2005}
{fermilab}

Participated in the high energy physics international collaboration for Large Hadron Collider (LHC) experiment. At the time United States team worked on the Compact Muon Solenoid  (CMS)  – part of the LHC experiment - building alignment system for muon detector.
\startitemize
\item Wrote technical specification for a data acquisition system.
\item Implemented multi-thread high performance server in Java controlling the system.
\item Designed and tested software to communicate with hardware via Cyclade TS consoles.
\item Database design for system configuration.
\item XML-RPC interface to the control server functionality.
\item Desktop program for system control using Swing
\stopitemize
Java 1.4, Swing, HSQL, Hibernate, XML-RPC, Python, Shell scripting
\page
{\bf Research Assistant} in 2001, 2002, 2004                                                                                                                    
\startitemize
\item Performed data analysis (regression analysis of statistical data from the detectors) of the data from optical sensors using ROOT package.
\item Developed software for above mentioned data analysis in C/C++ using ROOT framework.
\item Designed blueprints for and constructed hardware test bench for optical sensors testing and calibration.
\item Developed software in C and Python for optical sensors testing and calibrating.
\stopitemize 
C/C++, ROOT, Python, Shell

\Employment{InfoTelecom LLC -- Perm, Russia}
{Software Developer}
{Oct 2003 – Jul 2004}
{infotelecom}
Worked on the product software - highly customizable system of web-traffic statistics and monitoring
\startitemize
\item Designed and implemented website statistics collection system based on Javascript, servlets, and PL/SQL
\item Wrote graphs, charts, and diagram building library using Java2D and ImageIO, PL/SQL interface to it
\item Implemented website template based generation software
\item Developed website static content deployment tools using FTP
\stopitemize
Java 1.4, Java 2D, Oracle AS, Oracle 11g, PL/SQL, Shell Scripting, JavaScript

\Employment{iTech Software -- Perm, Russia}
{Software Developer}
{Oct 2002 – Sep 2003}
{itech}

\startitemize
\item Developed web interface using JSP and Java for payphones management.
\item Implemented Java code to work with IIS module in Visual C++ that controls network connections to the payphones.
\item Wrote testing scenarios and performed software unit testing.
\stopitemize
 Java 1.3, JNI, C/C++, JSP, JDBC, MS IIS, Interbase

\stoptext

