\setupcolors[state=start]
\usesymbols[uni]

\setupinteraction[state=start,
	title={Evgeniy N. Sharapov},
	subtitle={R\'esum\'e},
	author={Evgeniy N. Sharapov},
	keyword={resume}]

%% Layout
\setuppapersize[letter][letter]
\setuplayout[
  topspace=0cm,
  top=0cm,
  backspace=1cm,
  margin=1cm,
  rightedge=0cm,
  rightmargin=0.5cm,
  width=fit,
  % extend height of the body
  height=\dimexpr
    \paperheight-\topspace+\footerheight+\footerdistance-1cm\relax,
]

\setupwhitespace[small]

\definecolor[color1][r=1,b=0.4]
\definecolor[color2][r=1,g=0.4]

%% Fonts and such
\usemodule[simplefonts][size=10pt]
\usetypescript[palatino]
\setupbodyfont[palatino,10pt]
\setsansfont[Roboto]
\setmonofont[Consolas]
\setuphead[subject][textstyle=\bf, textcommand=\ss, deeptextcommand=\uppercase]

%% icons from the FontAwesome
\definefontsynonym[FontAwesome][fontawesome]
\definesymbol[phone][\getglyph{FontAwesome}{\char61589}]
\definesymbol[mobile][\getglyph{FontAwesome}{\char61707}]
\definesymbol[email][\getglyph{FontAwesome}{\char61664}]
%\definesymbol[email][\getglyph{FontAwesome}{\char113\kern-.66em\raise.25ex\hbox{\char51}}]
%\def\Check{{\tfa\symbol[box]}}
%\def\Checked{{\tfa\symbol[boxChecked]}}




%% Custom Commands


\starttext
%% Header
\midaligned { }
{ \scc Evgeniy N. Sharapov }
\wordright{
 {\rmx 3371, Mission Lake Dr, Apt 380, Orlando FL 32817}} \nowhitespace \\
\wordright{
 {\bf \symbol[mobile]}  (630) 448-0827 \cdot \  {\bf \symbol[email]} evgeniy.sharapov@gmail.com
 }

\hairline

%\subject{This is a test.}
%Serif typeface: regular, {\em italic}, {\bf bold} and {\em\bf bold italic} fonts.
%\subject{\color[color2]{This is another test}}
%{\ss Sans--serif typeface: regular, {\em italic}, {\bf bold} and {\bf\em bold italic} fonts.}
%{\tt Monospace typeface: regular, {\em italic}, {\bf bold} and {\bf\em bold italic} fonts.}
\loadmapfile [applesymbols25xx-apple-applesymbols.map]
\loadmapfile [applesymbols26xx-apple-applesymbols.map]
\definefontsynonym [UnicodeRegular25] [applesymbols25xx-AppleSymbols]
\definefontsynonym [UnicodeRegular26] [applesymbols26xx-AppleSymbols]
\setupsymbolset[Unicode Healing Signs]
%\showsymbolset[Unicode Warning Signs][n=4]
\symbol [Ankh]

\subject{Profile}
\startnarrower
Over 10 years of IT experience from administering servers to the scientific software development.

Certified Java Developer with knowledge and experience in an array of Java technologies (JNI, JDBC, J2EE, WebServices, JMS, etc.).

Database and Object-Oriented Architecture design for big and complex applications.
Proficient in a variety of programming languages, development tools, frameworks, and database management systems.

Organization of full software development life cycle: source code management, testing, quality assurance, building and deployment processes.

Ability to work alone with specifications and in a team (experience varies from small ones to multinational).

Solid educational background in engineering, statistics, mathematics, programming.
\stopnarrower

\subject{Qualifications}

Programming: Java, C/C++, Python, Clojure, Ruby

Development: Eclipse Platform, IBM RAD 6/7, Ant, Maven, JUnit, DbUnit, Subversion, Perforce, Git, CVS, VSS

Database: MS SQL Server 2000/2005, Oracle 9i/10g, SQLite, MySQL

Technologies: JNI, Swing, SWT, Java 2D, RMI, EJB, JTA, JMS, JNDI, JDBC, JSP, Servlets, XML-RPC, XML, XSLT,
XPath, JAX-RPC, WSDL4J, Axis, Hibernate, Apache Camel, Spring Framework, Struts, JBoss Drools, Websphere 5/6,
JBoss AS, IBM Websphere Process Server, IBM Business Process Manager

Web: JavaScript, (X)HTML, CSS, AJAX, SSL, Apache HTTP Server, Apache Tomcat, soapUI

Desktop: Microsoft Office: Project, Word, Excel, PowerPoint

Science: Matlab, Maple, Minitab, R System, ROOT, AMPL, ILOG CPLEX, LOQO

\subject{Experience}

StoneRiver, Inc.
Senior Software Development Engineer
Orlando, FL
Apr, 2013 --

\startitemize
	\item Client and technical support of multiple applications.
	\item Organization and execution of third party software compatibility testing.
	\item Development of usser interface, backend processes and auxiliary scripting
	\item Organization of the testing and release process.
	\item Websphere AS 7; JBoss 5, 6; Wildfly 8; AS/400; MS SQL Server; Java; Hibernate 3.5; Python; HTML5;Javascript;
\stopitemize


Click2Interact
Developer
Orlando, FL
Sep, 2012 -- Jan, 2013

\startitemize
	\item Educational platform for child development centers and pre-schools.
	\item Database design and business model prototyping.
	\item User interface using Twitter Bootstrap, jQuery and HTML5.
	\item Ruby On Rails 3.2, MySQL, RESTful Web-Services, Rackspace Cloud, jQuery, Twitter Bootstrap,
\stopitemize

Prognoz, http://www.prognoz.com/en/index.php
Lead Java Developer
Perm, Russia
Mar, 2012 -- Jul, 2012

\startitemize
	\item Tuning, installation and configuration of the IBM Websphere Process Server and Business Process Manager in cluster environment.
	\item Development of the business process integration in Integration Designer.
	\item Development of the "Meetings" application for the Moscow Government (documents exchange, meetings
and appointments scheduling, notification services) for mobile and desktop platform.
	\item Java 1.6, GWT, JPA 2, Web-Services, IBM Websphere Process Server and IBM BPM 8	
\stopitemize




\stoptext